Create year end summaries

### 2024-06-24 src/year-end-summary.Rmd
Added titanic-spline
Updated year-end-summary

```{r}
# Create yaml header
create_yaml <- function(yyyy) {
  glue(
    '---
     title: "Pages written in {yyyy}"
     source: new
     date: {yyyy}-12-31
     categories:
     - Blog post
     tags:
     - Website details
     output: html_document
     ---')
}
```

>>>>

```{r}
# Create yaml header
create_yaml <- function(yyyy) {
  glue(
    '---
     title: "Pages written in {yyyy}"
     source: new
     date: {yyyy}-12-31
     categories:
     - Blog post
     tags:
     - Website details
     output: html_document
     page_update: complete
     ---')
}
```
